---
title: "Analysis - Technology effects on spelling skill measurement"
format: html
---

## Setup

```{r}
library(tidyverse)
library(here)
library(easystats)
library(effectsize)
```

## Reusable functions

```{r}
path_data <- here("Data", "Processed")
```

## Read data

```{r}
data_paper <- read_csv(here(path_data, "data_paper_participant_level.csv"))
head(data_paper)
```

```{r}
data_tech <- read_csv(here(path_data, "data_pc_participant_level.csv"))
head(data_tech)
```

## Prepare data
### Merge data

#### Adds key to id condition

We add a column identifying the modality of the spelling measure to 
differentiate the condition after merging.

```{r}
data_paper <- data_paper |>
    mutate(condition = "paper")
str(data_paper)

data_tech <- data_tech |>
    mutate(condition = "tech")
str(data_tech)
```

#### merge data

```{r}
data_spelling <- bind_rows(data_paper, data_tech)
data_spelling
```

#### Check data

There should be 2 obs per participant. Looks good.
```{r}
data_spelling |>
    count(participant_id)
```

Each participant should have 1 observation per condition. Looks good.
```{r}
data_spelling |>
    count(participant_id, condition)
```

### Missing data

#### Check for missing data

No missing data
```{r}
data_spelling |>
    summarise_all(~ sum(is.na(.)))
```

### Convert variables to correct type

```{r}
data_spelling <- data_spelling |>
    mutate(condition = factor(condition))

data_spelling |>
    str()
```

## Analysis
### EDA
#### Univariate
##### All data

The data seems a little skewed toward higher scores.
```{r}
data_spelling |>
    ggplot(aes(x = total_correctness)) +
    geom_histogram(binwidth = 1)
```

##### Subdivide by condition

Both conditions seems about equally skewed toward higher scores.
```{r}
data_spelling |>
    ggplot(aes(x = total_correctness, fill = condition)) +
    geom_histogram(binwidth = 1, position = "dodge")
```

#### Bivariate
```{r}
viz_box <- data_spelling |>
    ggplot(aes(x = condition, y = total_correctness)) +
    geom_boxplot()

viz_box
```

```{r}
data_spelling |>
    ggplot(aes(x = condition, y = total_correctness)) +
    geom_violin()
```

### Inferential

#### Traditional model (t-test)
```{r}
basic_model <- t.test(
    total_correctness ~ condition,
    data = data_spelling,
    paired = TRUE
)

basic_model
```
