---
title: "Analysis - Technology effects on spelling skill measurement"
format: html
---

## Setup

```{r}
library(tidyverse)
library(here)
library(easystats)
```

```{r}
path_data <- here("Data", "Processed")
```

## Read data

```{r}
data_paper <- read_csv(here(path_data, "data_paper_participant_level.csv"))
head(data_paper)
```

```{r}
data_tech <- read_csv(here(path_data, "data_pc_participant_level.csv"))
head(data_tech)
```

## Merge data

### Adds key to id condition

We add a column identifying the modality of the spelling measure to 
differentiate the condition after merging.

```{r}
data_paper <- data_paper |>
    mutate(condition = "paper")
str(data_paper)

data_tech <- data_tech |>
    mutate(condition = "tech")
str(data_tech)
```

### merge data

```{r}
data_spelling <- bind_rows(data_paper, data_tech)
data_spelling
```

### Check data

There should be 2 obs per participant. Looks good.
```{r}
data_spelling |>
    count(participant_id)
```

Each participant should have 1 observation per condition. Looks good.
```{r}
data_spelling |>
    count(participant_id, condition)
```

## Missing data

### Check for missing data

No missing data
```{r}
data_spelling |>
    summarise_all(~ sum(is.na(.)))
```

## Convert variables to correct type

```{r}
data_spelling <- data_spelling |>
    mutate(condition = factor(condition))

data_spelling |>
    str()
```